---
title: "Living Network Meta-Analysis Tool"
---

```{r}
source("R/nma_functions.R")
dat <- load_pairwise_data()
```

This Quarto website is a static, reproducible version of the original Shiny prototype for a Living Network Meta-Analysis workflow. The original app logic has been decomposed into reusable R functions and rendered as an analysis website suitable for GitHub Pages.

## Project aim

The aim is to provide a transparent workflow for:

- preparing pairwise study-level data,
- fitting frequentist Network Meta-Analysis models with `netmeta`,
- exploring treatment networks,
- presenting league tables and ranking,
- documenting inconsistency checks,
- demonstrating node-merging sensitivity analysis.

## Current dataset snapshot

```{r}
knitr::kable(summarise_pairwise_data(dat))
```

## Recommended architecture

The full Shiny app should remain the interactive/server-oriented version. This Quarto version should be used as the reproducible thesis website and GitHub Pages output. Browser-side live modules can be added gradually after confirming that `netmeta` works reliably in webR.
