---
title: "Living Network Meta-Analysis Tool"
---

```{r}
source("R/nma_functions.R")
dat <- load_pairwise_data()
```

This website is an extension of my MSc thesis, developed using Quarto and Quarto Live.

It provides a static, reproducible version of the original Shiny prototype for a Living Network Meta-Analysis workflow. The original application logic has been decomposed into reusable R functions and rendered as an analysis website suitable for deployment through GitHub Pages.

In addition to the static analysis outputs, the website includes an interactive browser-side node-merging module powered by webR/WebAssembly, allowing users to explore selected sensitivity scenarios directly in the browser.

Last but not least, the developed application should be viewed as a methodological and technical blueprint rather than a production-ready Living NMA platform. Its purpose is to demonstrate how a reproducible Living Network Meta-Analysis workflow can be structured, documented, and partially explored through a static Quarto website with selected browser-side interactivity. 

## Project aim

The aim is to provide a transparent workflow for:

- preparing pairwise study-level data,
- fitting frequentist Network Meta-Analysis models with `netmeta`,
- exploring treatment networks,
- presenting league tables and ranking,
- documenting inconsistency checks,
- demonstrating node-merging sensitivity analysis.

## Current dataset snapshot

```{r}
knitr::kable(summarise_pairwise_data(dat))
```

## Recommended architecture

The full Shiny app should remain the interactive/server-oriented version. This Quarto version should be used as the reproducible thesis website and GitHub Pages output. Browser-side live modules can be added gradually after confirming that `netmeta` works reliably in webR.
